---
title: "week5 case2"
output: html_notebook
---

```{r setup}
library(readxl)

price_high = read_excel(
  "case2.xlsx", sheet = "high", range = "B2:D4", 
  col_names = FALSE
)
phdf = data.frame(price_high)

price_low = read_excel(
  "case2.xlsx", sheet = "low", range = "B2:D4", 
  col_names = FALSE
)
pldf = data.frame(price_low)

makeVector = function(dat){
  nc = ncol(dat)
  
  for (i in 1:nc){
    if (i == 1){
      mydata = dat[,1]
    }
    else{
      mydata = c(mydata, dat[,i])
    }
  }
  
  return (mydata)
}

makeData = function(vec){
  p = length(vec)
  
  mydata = data.frame(
    PRICE = factor(
      c(
        rep("H", p/2),
        rep("L", p/2)
    )),
    FUNC = factor(
      rep(c(
        rep("FEW", 3),
        rep("SOME", 3),
        rep("MANY", 3)
      ), 2)
    ),
    SALES = vec
  )
  
  return (mydata)
}

drawPrice = function(mydata){
  curve(
    dnorm(x, 
      mean(mydata[mydata$PRICE=="H", "SALES"]), 
      var(mydata[mydata$PRICE=="H", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=2, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$PRICE=="L", "SALES"]), 
      var(mydata[mydata$PRICE=="L", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=3, axes=F, ylab=""
  )
  
  par(xpd=T)
  legend(
    par()$usr[2], par()$usr[4],
    legend=c("H", "L"),
    pch=20, col=2:3
  )
}

drawFunc = function(mydata){
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="FEW", "SALES"]), 
      var(mydata[mydata$FUNC=="FEW", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=2, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="SOME", "SALES"]), 
      var(mydata[mydata$FUNC=="SOME", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=3, axes=F, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="MANY", "SALES"]), 
      var(mydata[mydata$FUNC=="MANY", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=4, axes=F, ylab=""
  )
  
  par(xpd=T)
  legend(
    par()$usr[2], par()$usr[4],
    legend=c("F", "S", "M"),
    pch=20, col=2:4
  )
}

salesv = append(makeVector(phdf), makeVector(pldf))
mydata = makeData(salesv)
```

#  1) Evaluate Interaction effect between price factor and featue factor
* H0 (Assumption)
    + population variance among factors are equal.
* H1 (Alternative hypothesis)
    + Not H0
* significant level: 5%

## 2 factor ANOVA (non repeated)
```{r}
emydata1a=aov(SALES~PRICE+FUNC, mydata)
summary(emydata1a)
```
H0 is denied at PRICE factor.  
It shows PRICE factor has different variability at 0.1% significant level.  
It means pricing has impact to sales.

## 2 factor ANOVA (repeated)
```{r}
emydata1b=aov(SALES~PRICE*FUNC, mydata)
summary(emydata1b)
```
H0 is denied at PRICE factor.  
It shows PRICE factor has different variability at 0.1% significant level.  
No interaction effect betrween PRICE and FUNC.  

```{r}
attach(mydata)
interaction.plot(PRICE, FUNC, SALES)
interaction.plot(FUNC, PRICE, SALES)
detach(mydata)
```
The chart shows synergy pattern among FUNC.  
The chart shows different gap of SALES betweeh PRICE factors at each FUNC factor.  

### Conclusion
Pricing has impact to sales.  
Interaction effect between pricing and feature has no inpact to sales.

#  2) Evaluate price factor on sales result
## 1 factor ANOVA
```{r}
emydata2=aov(SALES~PRICE, mydata)
summary(emydata2)
```
H0 is denied.  
SALES variances between PRICE H and L are different at 0.1% siginificant level.
Difference of pricing has impact to sales result.
```{r}
boxplot(SALES~PRICE, mydata)
```
```{r fig.width=7.5}
par(mar=c(5,4,4,5))
drawPrice(mydata)
```

#  3) Evaluate feature factor on sales result
## 1 factor ANOVA
```{r}
emydata3=aov(SALES~FUNC, mydata)
summary(emydata3)
```
H0 is not denied.
Difference of feature has no impact to sales result.
```{r}
boxplot(SALES~FUNC, mydata)
```
```{r fig.width=7.5}
par(mar=c(5,4,4,5))
drawFunc(mydata)
```
