---
title: "week5 case2"
output: html_notebook
---

```{r setup}
library(readxl)

price_high = read_excel(
  "case2.xlsx", sheet = "high", range = "B2:D4", 
  col_names = FALSE
)
phdf = data.frame(price_high)

price_low = read_excel(
  "case2.xlsx", sheet = "low", range = "B2:D4", 
  col_names = FALSE
)
pldf = data.frame(price_low)

makeVector = function(dat){
  nc = ncol(dat)
  
  for (i in 1:nc){
    if (i == 1){
      mydata = dat[,1]
    }
    else{
      mydata = c(mydata, dat[,i])
    }
  }
  
  return (mydata)
}

makeData = function(vec){
  p = length(vec)
  
  mydata = data.frame(
    PRICE = factor(
      c(
        rep("H", p/2),
        rep("L", p/2)
    )),
    FUNC = factor(
      rep(c(
        rep("FEW", 3),
        rep("SOME", 3),
        rep("MANY", 3)
      ), 2)
    ),
    SALES = vec
  )
  
  return (mydata)
}

drawPrice = function(mydata){
  curve(
    dnorm(x, 
      mean(mydata[mydata$PRICE=="H", "SALES"]), 
      var(mydata[mydata$PRICE=="H", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=2, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$PRICE=="L", "SALES"]), 
      var(mydata[mydata$PRICE=="L", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=3, axes=F, ylab=""
  )
  
  par(xpd=T)
  legend(
    par()$usr[2], par()$usr[4],
    legend=c("H", "L"),
    pch=20, col=2:3
  )
}

drawFunc = function(mydata){
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="FEW", "SALES"]), 
      var(mydata[mydata$FUNC=="FEW", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=2, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="SOME", "SALES"]), 
      var(mydata[mydata$FUNC=="SOME", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=3, axes=F, ylab=""
  )
  
  par(new=T)
  curve(
    dnorm(x, 
      mean(mydata[mydata$FUNC=="MANY", "SALES"]), 
      var(mydata[mydata$FUNC=="MANY", "SALES"])
    ),
    xlim=c(
      min(mydata$SALES), 
      max(mydata$SALES)
    ),
    col=4, axes=F, ylab=""
  )
  
  par(xpd=T)
  legend(
    par()$usr[2], par()$usr[4],
    legend=c("F", "S", "M"),
    pch=20, col=2:4
  )
}

salesv = append(makeVector(phdf), makeVector(pldf))
mydata = makeData(salesv)
```

#  1) Evaluate Interaction effect between price factor and featue factor
* significant level: 5%

1. Sum Sq: sum of square (level mean - grand mean)  
It shows variance between entire samples and factor sample.

2. Mean Sq: sum of square (level mean - grand mean) / freedom degree  
It shows mean of variance in sample.  

3. Residuals Sum Sq  
It shows variance of entier sample.

4. F value: #2 / #3
It shows ratio between variance between entire sample and factor sample.  

## 2 factor ANOVA (non repeated)
```{r}
emydata1a=aov(SALES~PRICE+FUNC, mydata)
summary(emydata1a)
```

## 2 factor ANOVA (repeated)
```{r}
emydata1b=aov(SALES~PRICE*FUNC, mydata)
summary(emydata1b)
```

```{r}
attach(mydata)
interaction.plot(PRICE, FUNC, SALES)
interaction.plot(FUNC, PRICE, SALES)
detach(mydata)
```
The chart shows synergy pattern among FUNC.  
The chart shows different gap of SALES betweeh PRICE factors at each FUNC factor.  

PRICE variance is bigger than Residuals (variance of entire sample).  
FUNC variance is smaller than Residuals.
In the other words, size of sales dispersion become bigger in the next order.  
1. PRICE (high and low)  
2. Residuals  
3. PRICE + FUNC  
4. FUNC (few, some and many)entier sample  

### Conclusion
Pricing has impact to sales.  
Interaction effect between pricing and feature has no inpact to sales.

#  2) Evaluate price factor on sales result
## 1 factor ANOVA
```{r}
emydata2=aov(SALES~PRICE, mydata)
summary(emydata2)
```
Mean variacne of PRICE is much bigger than Residuals.  
It shows sales dispersion between PRICE H and L is much different.

```{r}
boxplot(SALES~PRICE, mydata)
```
```{r fig.width=7.5}
par(mar=c(5,4,4,5))
drawPrice(mydata)
```

#  3) Evaluate feature factor on sales result
## 1 factor ANOVA
```{r}
emydata3=aov(SALES~FUNC, mydata)
summary(emydata3)
```
Mean variacne of FUNC is much smaller than Residuals.  
It shows sales dispersion among FUNC has not so big difference.
```{r}
boxplot(SALES~FUNC, mydata)
```
```{r fig.width=7.5}
par(mar=c(5,4,4,5))
drawFunc(mydata)
```
